%% acknowledgments.tex

% From mitthesis package
% Version: 1.02, 2024/06/19
% Documentation: https://ctan.org/pkg/mitthesis

\chapter*{Acknowledgments}
\pdfbookmark[0]{Acknowledgments}{acknowledgments}

I thank my advisor Wei Zhang for suggesting this project,
for his infinite patience and kindness throughout my entire time during graduate school,
and his seemingly instantaneous response times at all hours of the day
to the many, many stupid questions I asked.
Without the encouragement and support from Wei,
I would certainly never have completed my thesis or even passed my qualifying exams.

I also thank MIT itself for serving as my home for the last ten years,
and the math department for supporting me since I started graduate school.
I'd like to thank Barbara Peskin and Bjorn Poonen in particular
for some words of encouragement during my earlier years of PhD study,
and Theresa Cummings and Michele Gallarelli for their assistance throughout my studies.

I'd like to acknowledge my mentors during my undergraduate years,
particularly Joe Gallian and Ken Ono who had a great role in my journey.
Plus another thank-you to my mentors from high school, particularly
Cheryl Chiu, Zuming Feng, Beth Rothfuss, Zvezda Stankova, Paul Zeitz, and Yan Zhang;
Steve Dunbar's team in Lincoln, Nebraska which organized the USA Math Olympiad
and the Math Olympiad Summer Program;
and the coaches from the Taiwan IMO selection and training.

I thank the organizers and attendees of the fall 2024
learning seminar on arithmetic inner product formula
for inviting me to speak about my work-in-progress, and their helpful comments on it
leading directly to improvements to this thesis.

I thank Mark Sellke for proofreading a draft of this thesis
and finding several corrections.

Finally, I thank Ben Howard and Zhiwei Yun for serving on my thesis committee,
as well as David Vogan and Nike Sun for serving on my qualifying exams committee.

This work was partially supported by NSF GRFP under grant numbers 1745302 and 2141064.
