\chapter{General background}
\label{ch:background}

\section{Notation}
We provide a glossary of notation that will be used in this paper.
As mentioned in the introduction, $p > 2$ is a prime,
$F$ is a finite extension of $\QQ_p$,
and $E/F$ is an unramified quadratic field extension.

\begin{itemize}
  \ii For any $a \in E$, we let $\bar a$ denote the image of $a$
  under the nontrivial automorphism of $\Gal(E/F)$.
  (Hence $a = \bar a$ exactly when $a \in F$.)
  \ii Fix $\eps \in \OO_F^\times$ such that $E = F[\sqrt{\eps}]$.
  \ii Denote by $\varpi$ a uniformizer of $\OO_F$, such that $\bar \varpi = \varpi$.
  \ii Let $q \coloneqq |\OO_F/\varpi|$ be the residue characteristic.
  (Hence $|\OO_E / \varpi| = q^2$.)
  \ii Let $v$ be the associated valuation for $\varpi$.
  \ii Let $\eta$ be the quadratic character attached to $E/F$ by class field theory,
  so that $\eta(x) = -1^{v(x)}$.
  \ii $\VV_n^+$ denotes a split $E/F$-Hermitian space of dimension $n$ (unique up to isomorphism).
  \ii Let $\beta$ denote the $n \times n$ antidiagonal matrix
  \[ \beta \coloneqq \begin{pmatrix} && 1 \\ & \iddots \\ 1 \end{pmatrix} \]
  and pick the basis of $\VV_n^+$ such that the Hermitian form on $\VV_n^+$ is given by
  \[ \VV_n^+ \times \VV_n^+ \to E \qquad (x,y) \mapsto x^\ast \beta y. \]
  \ii Set
  \[ \U(\VV_n^+) = \{ g \in \GL_n(\OO_E) \mid g^\ast \beta g = \beta\} \]
  the unitary group over $\VV_n^+$.
  Note that $\beta$ is \emph{antidiagonal}, in contrast to the convention $\beta = \id_n$
  that is often used for unitary matrices with entries in $\CC$.
  The natural hyperspecial maximal compact subgroup
  is \[ \U(\VV_n^+) \cap \GL_n(\OO_E). \]
  In some parts of the paper we abbreviate $G = \U(\VV_n^+)$ and $K = \U(\VV_n^+) \cap \GL_n(\OO_E)$
  following the convention in \cite{ref:AFLspherical}.
  \ii Let $K' \coloneqq \GL_n(\OO_E)$ denote the hyperspecial maximal compact subgroup of $G' \coloneqq \GL_n(E)$.
  \ii Let $\VV_n^-$ denote the non-split $E/F$-Hermitian space of dimension $n$
  (unique up to isomorphism), and $\U(\VV_n^-)$ the corresponding unitary group.
  This space will be realized in \Cref{ch:geo}.
\end{itemize}

\section{Intersection of disks in an ultrametric space}
The following two lemmas will be useful for both versions of the orbital integral.
It is a slight rephrasing of \cite[Lemma 4.4]{ref:AFL}.

\begin{lemma}
  \label{lem:volume}
  Let $\xi \in \OO_E^\times$, $\rho \in \ZZ$, and $n \ge \max(\rho, 1)$ an integer.
  Then
  \begin{align*}
    &\Vol\left( \left\{ x \in E \mid v(1-x \bar x) = n,
      \; v(x-\xi) \ge \rho \right\} \right) \\
    &=
    \begin{cases}
      0 & \text{if } v(1-\xi\bar\xi) < \rho \\
      q^{-n}(1-q^{-2}) & \text{if } \rho \le 0 \\
      q^{-(n+\rho)}(1-q\inv) & \text{if } v(1-\xi\bar\xi) \ge \rho \ge 1.
    \end{cases}
  \end{align*}
\end{lemma}
\begin{proof}
  When $\rho \le 0$, the condition $v(x - \xi) \ge \rho$ is vacuously true,
  so we just are computing
  \[ \Vol\left( \left\{ x \in E \mid v(1-x \bar x) = n \right\} \right). \]
  However, in general for any Schwartz function $\psi$ on $E$ we have an identity
  \begin{equation}
    \int_E \psi(x) \odif x
    = \frac{1}{1-q\inv} \int_{y \in F} \int_{t \in \OO_E^\times}
    \psi\left( x_t \cdot \frac{y}{\bar y} \right) \odif y \odif t
    \label{eq:schwartz}
  \end{equation}
  where $x_t$ is any choice of element $x_t \in E$ such that $t = x_t \bar{x_t}$
  (see the proof of \cite[Lemma 4.4]{ref:AFL}).
  Note the measures here are additive despite $t \in \OO_E^\times$.
  So if one selects
  \[ \psi(x) = \mathbf{1}_{v(1 - \Norm(x)) = n} \]
  then we get
  \begin{align*}
    \Vol\left( \left\{ x \in E \mid v(1-x \bar x) = n \right\} \right)
    &= \frac{1}{1-q\inv} \int_{t \in F} \int_{y \in \OO_E^\times}
    \mathbf{1}_{v\left( 1 - \Norm\left(x_t \cdot \frac{y}{\bar y} \right) \right) = n} \odif y \odif t \\
    &= \frac{1}{1-q\inv} \int_{t \in F} \int_{y \in \OO_E^\times}
    \mathbf{1}_{v\left( 1 - t \right) = n} \odif y \odif t \\
    &= \frac{\Vol_E(\OO_E^\times)}{1-q\inv} \cdot \Vol_F(1 + \varpi^{-n} \OO_F^\times) \\
    &= \frac{1 - \frac{1}{q^2}}{1-q\inv}
      \cdot \left( q^{-n} \cdot \left( 1 - \frac 1q \right) \right) \\
    &= q^{-n} (1-q^{-2}).
  \end{align*}
  The case $\rho > 0$ is proved in \cite[Lemma 4.4]{ref:AFL}
  using the same method of using \eqref{eq:schwartz}.
\end{proof}

We also comment on the well-known fact that in an ultrametric space,
any two disks are either disjoint or one is contained in the other.
(In other words, the Mastercard logo cannot be drawn. See \Cref{fig:no_mastercard}.)
\begin{lemma}
  Choose $\xi_1, \xi_2 \in E$ and $\rho_1 \geq \rho_2$.
  Consider the two disks:
  \begin{align*}
    D_1 &= \left\{ x \in E \mid v(x-\xi_1) \ge \rho_1 \right\} \\
    D_2 &= \left\{ x \in E \mid v(x-\xi_2) \ge \rho_2 \right\}.
  \end{align*}
  Then, if $v(\xi_1-\xi_2) \geq \rho_2$, we have $D_1 \subseteq D_2$.
  If not, instead $D_1 \cap D_2 = \varnothing$.
  \label{lem:no_mastercard}
\end{lemma}
\begin{proof}
  Because $E$ is an ultrametric space and $\Vol(D_1) \leq \Vol(D_2)$,
  we either have $D_1 \subseteq D_2$ or $D_1 \cap D_2 = \varnothing$.
  The latter condition checks which case we are in by testing if $\xi_1 \in D_2$,
  since $\xi_1 \in D_1$.
\end{proof}

\begin{figure}
\centering
\begin{asy}
  defaultpen(fontsize(12pt));
  size(7cm);
  pair O1 = 0.57*dir(-30);
  pair O2 = (0,0);
  real r1 = 0.4;
  real r2 = 1;
  filldraw(circle(O2, r2), rgb(0.9, 0.9, 0.9));
  filldraw(circle(O1, r1), rgb(0.8, 0.8, 0.9));
  pair P1 = O1+r1*dir(230);
  pair P2 = O2+r2*dir( 70);
  draw(O1--P1);
  draw(O2--P2);
  dot("$\xi_1$", O1, dir(90));
  dot("$\xi_2$", O2, dir(180));
  label("$q^{-\rho_1}$", midpoint(O1--P1), dir(P1-O1)*dir(90));
  label("$q^{-\rho_2}$", midpoint(O2--P2), dir(P2-O2)*dir(90));
\end{asy}
\caption{Figure corresponding to \Cref{lem:no_mastercard}.}
\label{fig:no_mastercard}
\end{figure}

We package both of these results together
lemma that will be used repeatedly.
\begin{lemma}
  \label{lem:quadruple_ineq}
  Let $\xi_1, \xi_2 \in \OO_E^\times$ and let $\rho_1 \ge \rho_2$ be integers.
  Also let $n \ge \max(\rho_1, 1)$ be an integer.
  Then the set of points $x \in E$ satisfying all of the equations
  \begin{align*}
    v(x - \xi_1) &\ge \rho_1 \\
    v(x - \xi_2) &\ge \rho_2 \\
    v(1 - x \ol x) &= n
  \end{align*}
  has positive volume if and only if
  \[ v(1 - \xi_1 \bar{\xi_1}) \ge \rho_1, \qquad \rho_2 \le v(\xi_1 - \xi_2). \]
  In that case, the volume is equal to
  \[
    \begin{cases}
      q^{-(n+\rho_1)}(1-q\inv) & \text{if } \rho_1 \ge 1 \\
      q^{-n}(1-q^{-2}) & \text{if } \rho_1 \le 0.
    \end{cases}
  \]
\end{lemma}
In the situation where $\xi_i \notin \OO_E^\times$,
the quantity $v(x-\xi_i) = \min(0, v(\xi_i))$
becomes independent of the value of $x$,
and so \Cref{lem:quadruple_ineq} becomes unnecessary
(\Cref{lem:volume} will suffice).
We will deal with this situation when it arises;
it turns out this will only occur when $v(b) \neq 0$.

\section{The spaces $S_n(F)$ and $S_n(F) \times V'_n(F)$}
For the analytic side of the two AFL conjectures we investigate,
the following two spaces will be used as inputs to our weighted orbital integrals.
\begin{definition}
  [{\cite[(4.10)]{ref:highdim2024}}]
  We define the symmetric space
  \[ S_n(F) \coloneqq \left\{ g \in \GL_n(E) \mid g \bar g = \id_n \right\}. \]
  It has a natural left action of $\GL_n(E)$ by
  \begin{align*}
    \GL_n(E) \times S_n(F) &\to S_n(F) \\
    g \cdot \gamma &\coloneqq g \gamma \bar g^{-1}.
  \end{align*}
\end{definition}

\begin{definition}
  [{\cite[(4.11)]{ref:highdim2024}}]
  We set
  \[ V'_n(F) \coloneqq F^n \times (F^n)^\vee \]
  where $-^\vee$ denotes the $F$-dual space, i.e., $(F^n)^\vee = \Hom_F(F^n, F)$.
  Then we may also consider the augmented space
  \[ S_n(F) \times V'_n(F) \]
  If we identify $F^n$ with column vectors of length $n-1$ and $(F^n)^\vee$
  with row vectors of length $n$ then we have a left action of $\GL_n(F)$ by
  \begin{align*}
    \GL_n(F) \times (S_n(F) \times V'_n)(F)
    &\to S_n(F) \times V'_n(F) \\
    h \cdot (\gamma, \uu, \vv^\top)
    &\coloneqq (h \gamma h^{-1}, h\uu, \vv^\top h^{-1}).
  \end{align*}
  Note that according to the embedding
  \begin{align*}
    S_n(F) \times V'_n(F)
    &\hookrightarrow \GL_{n+1}(E) \\
    (\gamma, \uu, \vv^\top)
    &\mapsto \begin{pmatrix} \gamma & \uu \\ \vv^\top & 0 \end{pmatrix}
  \end{align*}
  we can consider elements of $S_n(F) \times V'_n(F)$ as elements of $\GL_{n+1}(E)$ too.
  In that case the action of $h \in \GL_{n+1}(F)$
  coincides with $h \cdot g \mapsto hg\bar{h}^{-1}$ as well.
\end{definition}

\begin{definition}
  For brevity, let
   \[ K'_S \coloneqq S_n(F) \cap \GL_n(\OO_F). \]
\end{definition}

\section{Definition of Hecke algebra}
We reminder the reader the definition of a Hecke algebra.
For this subsection, $G$ will denote \emph{any}
unimodular locally compact topological group,
and $K$ any closed subgroup of $G$.

\begin{definition}
  The \emph{Hecke algebra}
  \[ \HH(G, K) \coloneqq \QQ[K \backslash G \slash K] \]
  is defined as the space of compactly supported $K$-bi-invariant
  locally constant functions on $G$.

  Given two such functions $f_1$ and $f_2$ in $\HH(G,K)$,
  one can consider define the convolution
  \[ (f_1 \ast f_2)(g) \coloneqq \int_G f_1(g\inv x) f_2(x) \; \odif x \]
  which makes $\HH(G, K)$ into a $\QQ$-algebra,
  whose identity element is $\mathbf{1}_K$.
\end{definition}

In other sources, this may be denoted $\HH_K(G)$ or even just $\HH_K$.
(So what is written in $\HH_{K'^\flat \otimes K'}$ in other places
will be written as $\HH(G'^\flat \otimes G', K'^\flat \otimes K')$ here).

In the case where $G$ is a reductive Lie group and
$K$ is the maximal compact subgroup
(or more generally whenever $(G,K)$ is a Gelfand pair),
this Hecke algebra is actually commutative.

\section{The specific Hecke algebras $\HH(\GL_n(E))$ and $\HH(\U(\VV_n^+))$ and the module $\HH(S_n(F))$}
For our purposes, we define shorthands for two specific Hecke algebras
that will come up consistently:
\begin{align*}
  \HH(\GL_n(E)) &\coloneqq \HH(\GL_n(E), \GL_n(\OO_E)) \\
  \HH(\U(\VV_n^+)) &\coloneqq \HH(\U(\VV_n^+), \U(\VV_n^+) \cap \GL_n(\OO_E))
\end{align*}
Note that $\GL_n(\OO_E)$ and $\U(\VV_n^+) \cap \GL_n(\OO_E)$
are the natural hyperspecial maximal compact subgroups of $\GL_n(E)$ and $\U(\VV_n^+$),
respectively.

Now the symmetric space $S_n(F)$ is not a group,
so it does not make sense to define the same thing here.
Nevertheless, we introduce
\[ \HH(S_n(F)) \coloneqq \mathcal C_{\mathrm{c}}^{\infty}(S_n(F))^{K'} \]
as the set of smooth compactly supported functions on $S_n(F)$
which are invariant under the action of $K' \subseteq G'$;
this is an $\HH(\GL_n(E))$-module,
where the action of $f \in \HH(\GL_n(E))$ on $\phi \in \HH(S_n(F))$ is given by
\[ (f \cdot \phi)(\gamma) \coloneqq \int_G f(g) \phi(g \cdot \gamma) \odif g \]
for $\gamma \in S_n(F)$.
This does \textbf{not} have a multiplication structure at the moment, \emph{a priori}.
However, we will later (in \Cref{ch:satake}) give an isomorphism from $\HH(S_n(F))$
to $\HH(\U(\VV_n^+))$ as $\QQ$-vector spaces;
since the latter is a $\QQ$-algebra, it can be used to impose a ring structure on $\HH(S_n(F))$.

Throughout this paper, to be consistent with the notation, we denote
\begin{itemize}
  \ii elements of $\HH(\U(\VV_n^+))$ using $f$ or $f_i$ or similar
    (i.e.\ lowercase Roman letters);
  \ii elements of $\HH(\GL_n(E))$ by $f'$ or $f'_i$ or similar
    (i.e.\ lowercase Roman letters with apostrophes);
  \ii elements of $\HH(S_n(F))$ by $\phi$ or $\phi_i$
    (i.e.\ lowercase Greek letters).
\end{itemize}
